### 2023-12-07 Paper/tex/bifacial_peak_shaving_paper.tex
move images location

\begin{figure}
\centering
\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/tech_shaving.png}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/econ_shaving.png}
\caption{technical peak shaving}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=5.14583in,height=\textheight]{17019217180021.png}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=6.59375in,height=\textheight]{17019217180102.png}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=4.91667in,height=\textheight]{17019217180163.png}
\caption{}
\end{figure}

@@

\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/total retail electric cost.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/reduction in total retail electric cost.png}

@@

\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/single day of peak shaving 1.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/.images/bifacial_peak_shaving_paper.assets/single day of peak shaving 2.png}

>>>>

\begin{figure}
\centering
\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/tech_shaving.png}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/econ_shaving.png}
\caption{technical peak shaving}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=5.14583in,height=\textheight]{17019611651481.png}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=6.59375in,height=\textheight]{17019611651552.png}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=4.91667in,height=\textheight]{17019611651613.png}
\caption{}
\end{figure}

@@

\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/total retail electric cost.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/reduction in total retail electric cost.png}

@@

\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/single day of peak shaving 1.png}\includegraphics{/home/mjw/Code/Bifacial-solar-and-peakshaving/Paper/images/single day of peak shaving 2.png}
